### 2017-06-07 Manuscript/SW_early_life_telomeres_FULL.Rmd
Edits

#Set some options
options(na.action='na.fail')
opts_knit$set(root.dir = '..')
opts_chunk$set(echo=FALSE,
               warning=FALSE,
               message=FALSE,
               fig.width=8,
               fig.height=8)

>>>>

#Set some options
options(na.action='na.fail')
opts_knit$set(root.dir = '..')
opts_chunk$set(echo=FALSE,
               warning=FALSE,
               message=FALSE,
               cache = TRUE,
               fig.width=8,
               fig.height=8)
